---
title: Fibroscope_Analysis_1
author: Serdar Korur
date: '2019-10-11'
output: html_document
---

We will dig in the data from a recent [article](https://www.atsjournals.org/doi/pdf/10.1164/rccm.201712-2410OC) which explored lung cells from Pulmonary fibrosis patients by using scRNAseq.


* **Pulmonary fibrosis** is a progressive scarring of the lung tissue leading to death within 3-4 years.
* **Current therapies does not increase the survival** 
* Many Biotech companies are developing **novel drugs**


---> [Download Single Cell RNA seq data](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3489196)

```{bash, eval=FALSE}
curl -O https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE122960&format=file 
tar -xvf GSE122960_RAW.tar --directory data/
```

I renamed the files for easy typing. 

### Reading multiple h5 files and Creating a Seurat Object for all of them:

```{r Reading multiple h5 files, cache=TRUE}
library(Seurat)
# Create a Vector containing names of all of the files you want to read in the folder 
vector_h5 <- c("Donor_01.h5",   "Donor_02.h5",   "Donor_03.h5", 
               "Donor_04.h5",   "Donor_05.h5",   "Donor_06.h5", 
               "Donor_07.h5",   "Donor_08.h5",   "Cryo_01.h5", 
               "HP_01.h5",      "IPF_01.h5",     "IPF_02.h5", 
               "IPF_03.h5",     "IPF_04.h5",     "Myo_01.h5",
               "SSc_01.h5", "SSc_02.h5")

path <- file.path("data/FILTERED", vector_h5)

# Read all h5 files with Read10X_h5 function, and load dome on a list named GSE122690

GSE122690 <- lapply(path, Read10X_h5)
```

```{r For labeling seurat objects, cache=TRUE}
# Create Seurat Object with labels
# I add here two labels (L1, L2) so that we can easily compare single patients and or compare groups i.e. healthy vs donor.
# DONORS

D01 <- CreateSeuratObject(counts = GSE122690[[1]], project = "Donor")
D01$L1 <- "D01"
D01$L2 <- "Don"

D02 <- CreateSeuratObject(counts = GSE122690[[2]], project = "Donor")
D02$L1 <- "D02"
D02$L2 <- "Don"

D03 <- CreateSeuratObject(counts = GSE122690[[3]], project = "Donor")
D03$L1 <- "D03"
D03$L2 <- "Don"

D04 <- CreateSeuratObject(counts = GSE122690[[4]], project = "Donor")
D04$L1 <- "D04"
D04$L2 <- "Don"

D05 <- CreateSeuratObject(counts = GSE122690[[5]], project = "Donor")
D05$L1 <- "D05"
D05$L2 <- "Don"

D06 <- CreateSeuratObject(counts = GSE122690[[6]], project = "Donor")
D06$L1 <- "D06"
D06$L2 <- "Don"

D07 <- CreateSeuratObject(counts = GSE122690[[7]], project = "Donor")
D07$L1 <- "D07"
D07$L2 <- "Don"

D08 <- CreateSeuratObject(counts = GSE122690[[8]], project = "Donor")
D08$L1 <- "D08"
D08$L2 <- "Don"


# Patients

Cry01 <- CreateSeuratObject(counts = GSE122690[[9]], project = "PF")
Cry01$L1 <- "Cry01"
Cry01$L2 <- "Pat"

HP01 <- CreateSeuratObject(counts = GSE122690[[10]], project = "PF")
HP01$L1 <- "HP01"
HP01$L2 <- "Pat"

# IPF

IPF01 <- CreateSeuratObject(counts = GSE122690[[11]], project = "PF")
IPF01$L1 <- "IPF1"
IPF01$L2 <- "Pat"

IPF02 <- CreateSeuratObject(counts = GSE122690[[12]], project = "PF")
IPF02$L1 <- "IPF2"
IPF02$L2 <- "Pat"

IPF03 <- CreateSeuratObject(counts = GSE122690[[13]], project = "PF")
IPF03$L1 <- "IPF3"
IPF03$L2 <- "Pat"

IPF04 <- CreateSeuratObject(counts = GSE122690[[14]], project = "PF")
IPF04$L1 <- "IPF4"
IPF04$L2 <- "Pat"

Myo01 <- CreateSeuratObject(counts = GSE122690[[15]], project = "PF")
Myo01$L1 <- "Myo01"
Myo01$L2 <- "Pat"

SSc01 <- CreateSeuratObject(counts = GSE122690[[16]], project = "PF")
SSc01$L1 <- "SSc01"
SSc01$L2 <- "Pat"

SSc02 <- CreateSeuratObject(counts = GSE122690[[17]], project = "PF")
SSc02$L1 <- "SSc02"
SSc02$L2 <- "Pat"
```


```{r merging all 16 labelled samples (FiBL)}

# Merging Fibrosis Big with labels (FiBL)

FiBL <- merge(D01, y = c(D02,  D03, D04, D05, D06, D07, 
                        D08, HP01, IPF01, IPF02, IPF03, 
                        IPF04, Myo01, SSc01, SSc02),
              add.cell.ids = c("D01" , "D02" , "D03" , "D04" , "D05" , "D06" , "D07" , "D08" , "HP01" , "IPF01" , "IPF02" , "IPF03" , "IPF04" , "Myo01" , "SSc01" , "SSc02"),  project = "FiBL")
```


```{Start analyzing}

```

